Magnetized accretion disks around Kerr black holes with scalar hair - I. Constant angular momentum disks

### 2018-11-06 paper_prd.tex
reference and comment on the original grid

Before starting to build the disc, it is important to note that we need a sufficiently fine numerical grid in order to fully capture the behaviour of the physical magnitudes at the inner region of the disc. For that reason, we use a non-uniform grid $(r, \theta)$ with a domain $[r_{\mathrm{H}}, 199.2] \times [0, \pi/2]$ and a number of points $N_r \times N_{\theta} = 2500 \times 300$. This means a radial resolution of $\simeq 0.001$ at the location of the disc centre. \sg{This is a rough approximmation, as this exact number depend on the horizon radius $r_{\mathrm{H}}$ and on the specific model. Nevertheless, the value of the resolution is much better at the cusp, specially if the disk is very close to the horizon (for instance in the $a = 0.9999$ Kerr case). Maybe we should clarify this, as these high spin cases need a very high radial resolution. Also, it may be important to note that it seems that we have not angular resolution enough to resolve the morphology of the disk in these extreme cases (see the 2D perimeteral plots). But I think this should go in the results section.} \sg{I am not sure if we have to tell something about the \it{real} initial data} (i.e. the data provided by Carlos).
Next, we first need to find $l_{\mathrm{mb}}$ and $r_{\mathrm{mb}}$ as the minimum of Eq.~\eqref{eq:mb_ang_mom} and the location of said minimum in terms of the radial coordinate respectively. Once we have that, we can compute the total potential distribution as
\begin{equation}
W(r,\theta) \equiv \ln |u_t| = \frac{1}{2} \ln \left| \frac{g_{t\phi}^2-g_{tt}g_{\phi\phi}}{g_{\phi\phi}+2g_{t\phi}l+g_{tt}l^2} \right|.
\end{equation}
With the total potential distribution, we can compute the location of the cusp $r_{\mathrm{cusp}}$ and the centre $r_{\mathrm{c}}$ as the extrema (maximum and minimum respectively) of the total potential in the equatorial plane. Also, we set $r_{\mathrm{in}} = r_{\mathrm{cusp}}$. For our choice of angular momentum distribution, this also means $W_{\mathrm{in}} = 0$.
Having now the total potential distribution and the characteristic radii of the disc, we can start to compute the thermodynamical quantities in the disc.
First of all, we compute the polytropic constant $K$ evaluating Eq.~\eqref{eq:final} at the centre
\begin{equation}\label{eq:to_solve_K}
W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho_{\mathrm{c}}^{\Gamma -1}\right) + \frac{q}{q-1} \frac{K\rho_{\mathrm{c}}^{\Gamma}}{\beta_{\mathrm{m_c}} (\rho_{\mathrm{c}} + \frac{K\Gamma\rho_{\mathrm{c}}^{\Gamma}}{\Gamma-1})} =0\,
\end{equation}
where we have used the definition of magnetic pressure and the definition of the magnetisation parameter $\beta$. Using its corresponding definitions, we can also compute $h_{\mathrm{c}}$, $p_{\mathrm{c}}$, $p_{\mathrm{m_c}}$ and the constant of the magnetic EOS $M$.
With both $K$ and $M$ obtained, we can now compute the thermodynamical quantities in all our numerical domain. For points with $W(r, \theta) > 0$ we set $\rho = p = p_{\mathrm{m}} = 0$ and for points with $W_{\mathrm{c}} < W(r, \theta) < 0$, we write Eq.~\eqref{eq:final} as
\begin{equation}\label{eq:to_solve_rho}
W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}M(\mathcal{L}(\rho + \frac{K\Gamma \rho^{\Gamma}}{\Gamma - 1}))^{q-1}=0,\,
\end{equation}
to compute the rest-mass density $\rho$ of said point. Then, we can use again Eqs.~\eqref{eq:eos_fluid} and~\eqref{eq:eos_mag_tilde} and the definition of the specific enthalpy to compute the distribution of $p$, $p_{\mathrm{m}}$ and $h$.

>>>>

Before starting to build the disc, it is important to note that we need a sufficiently fine numerical grid in order to fully capture the behaviour of the physical magnitudes at the inner region of the disc. For that reason, we use a non-uniform grid $(r, \theta)$ with a domain $[r_{\mathrm{H}}, 199.2] \times [0, \pi/2]$ and a number of points $N_r \times N_{\theta} = 2500 \times 300$. This grid is an interpolated version of the original data, obtained as a result by~\cite{Herdeiro:2015b}. The original grid is a uniform grid ($x$, $\theta$) (where $x$ is a compactified radial coordinate) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_x \times N_{\theta} = 251 \times 30$\footnote{Some samples are presented in~\cite{grav_web}}. To obtain our grid, we use the coordinate change provided in~\cite{grav_web} and interpolate the initial grid with order 3 splines. \sg{This is a rough approximmation, as this exact number depend on the horizon radius $r_{\mathrm{H}}$ and on the specific model. Nevertheless, the value of the resolution is much better at the cusp, specially if the disk is very close to the horizon (for instance in the $a = 0.9999$ Kerr case). Maybe we should clarify this, as these high spin cases need a very high radial resolution. Also, it may be important to note that it seems that we have not angular resolution enough to resolve the morphology of the disk in these extreme cases (see the 2D perimeteral plots). But I think this should go in the results section.} \sg{I am not sure if we have to tell something about the \it{real} initial data} (i.e. the data provided by Carlos).
Next, we first need to find $l_{\mathrm{mb}}$ and $r_{\mathrm{mb}}$ as the minimum of Eq.~\eqref{eq:mb_ang_mom} and the location of said minimum in terms of the radial coordinate respectively. Once we have that, we can compute the total potential distribution as
\begin{equation}
W(r,\theta) \equiv \ln |u_t| = \frac{1}{2} \ln \left| \frac{g_{t\phi}^2-g_{tt}g_{\phi\phi}}{g_{\phi\phi}+2g_{t\phi}l+g_{tt}l^2} \right|.
\end{equation}
With the total potential distribution, we can compute the location of the cusp $r_{\mathrm{cusp}}$ and the centre $r_{\mathrm{c}}$ as the extrema (maximum and minimum respectively) of the total potential in the equatorial plane. Also, we set $r_{\mathrm{in}} = r_{\mathrm{cusp}}$. For our choice of angular momentum distribution, this also means $W_{\mathrm{in}} = 0$.
Having now the total potential distribution and the characteristic radii of the disc, we can start to compute the thermodynamical quantities in the disc.
First of all, we compute the polytropic constant $K$ evaluating Eq.~\eqref{eq:final} at the centre
\begin{equation}\label{eq:to_solve_K}
W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho_{\mathrm{c}}^{\Gamma -1}\right) + \frac{q}{q-1} \frac{K\rho_{\mathrm{c}}^{\Gamma}}{\beta_{\mathrm{m_c}} (\rho_{\mathrm{c}} + \frac{K\Gamma\rho_{\mathrm{c}}^{\Gamma}}{\Gamma-1})} =0\,
\end{equation}
where we have used the definition of magnetic pressure and the definition of the magnetisation parameter $\beta$. Using its corresponding definitions, we can also compute $h_{\mathrm{c}}$, $p_{\mathrm{c}}$, $p_{\mathrm{m_c}}$ and the constant of the magnetic EOS $M$.
With both $K$ and $M$ obtained, we can now compute the thermodynamical quantities in all our numerical domain. For points with $W(r, \theta) > 0$ we set $\rho = p = p_{\mathrm{m}} = 0$ and for points with $W_{\mathrm{c}} < W(r, \theta) < 0$, we write Eq.~\eqref{eq:final} as
\begin{equation}\label{eq:to_solve_rho}
W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}M(\mathcal{L}(\rho + \frac{K\Gamma \rho^{\Gamma}}{\Gamma - 1}))^{q-1}=0,\,
\end{equation}
to compute the rest-mass density $\rho$ of said point. Then, we can use again Eqs.~\eqref{eq:eos_fluid} and~\eqref{eq:eos_mag_tilde} and the definition of the specific enthalpy to compute the distribution of $p$, $p_{\mathrm{m}}$ and $h$.
